Truth space method for caching database queries

### 2014-12-06 english_version/Elsevier/paper_main.tex
Elsevier version added; gitignore updated.

% This document is created with a help of
% v2-acmsmall-sample.tex sample file, v1.3 - March 2012

\documentclass[prodmode,acmtods]{acmsmall} % Aptara syntax

\usepackage{amssymb,amsmath}
%\usepackage{amsfonts}
%\usepackage{algorithm}
%\usepackage{xcolor}
%\usepackage{textcomp}
\newtheorem{note}{Note}
\newtheorem{statement}{Statement}
\def \eval #1#2{\left.#1\right\vert_{#2}}
\def \<#1> {\langle #1 \rangle}
\def \n #1{\mathit{#1}}

% Package to generate and customize Algorithm as per ACM style
\usepackage[ruled]{algorithm2e}
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

% Metadata Information
\acmVolume{9}
\acmNumber{4}
\acmArticle{39}
\acmYear{2010}
\acmMonth{3}

% Document starts
\begin{document}

% Title portion
\title{Truth space method for caching database queries}

@@

\category{H.2.3, H.2.4}{Database Management}{Languages, Systems}

\terms{Languages, Theory, Performance}

\keywords{Relational database, Truth space, Intermediate Data View, Logical
formula}

\maketitle

\section{Introduction}
In this paper we discuss the use of data views that are
cached on the client's computer. We assume client-server environment with
server based Relational Database (RDB). The cache stores query results in order
to provide maximum usage of saved data in subsequent queries.

@@

Query 1: List of students studying physics, whose ID is bigger than 210:
$$P_1 = \pi_{X_1}(\sigma_{F_1} (R_1 \Join R_2)),$$
where $\pi_{X_1}$ -- projection operation over the set of attributes
$X_1 = \{\text{Stud\_ID}, \text{Stud\_Name}, \text{Group}, \text{Course}\}$,
$\sigma$ -- selecting operation,
$F_1$ -- logical formula: $(\text{Stud\_ID} > 210\ \&\ \text{Course} =
\text{Physics})$, $\Join$ --natural join.

Query 2: Examination sheets of the group M10:
$$P_2 = \pi_{X_2}(\sigma_{F_2} (R_1 \Join R_3)),$$
where
$X_2 = \{\text{Stud\_ID}, \text{Group}, \text{Course}, \text{Score}\}$, $F_2$
-- logical condition: $(\text{Group}=\text{M10})$.

@@

\begin{multline*}
\mathcal{A} = Dom(\text{Stud\_ID})\times Dom(\text{Stud\_Name}) \times
Dom(\text{Group}) \times Dom(\text{Room\_ID}) \times\\
\times Dom(\text{Course}) \times Dom(\text{Score}) = \{205, 315, 461\} \times
\{\text{Rachel Davis, Noam Angrist},\\
\text{Cameron McCord}\} \times\{\text{M10, M11}\} \times \{100, 101, 102, 103\}
\times \{\text{Physics, Chemistry}\} \times\\ \times \{70, 80, 90\}
\end{multline*}

Obviously, without constraints this set represents more states than DB can have.
For example, each student has his/her own ID, whereas there are 3 corresponding
IDs for each student in $\mathcal{A}$: $\{205, 315, 461\}\times \{\text{Rachel
Davis, Noam Angrist, Cameron McCord}\}$.

@@

\begin{multline*}
F_1 = (\text{Stud\_ID} > 210\ \&\ \text{Course} = \text{Physics}\ \&\
\text{Stud\_Name}\ \textit{IN}\ \{\text{Rachel Davis, Noam}\\
\text{Angrist, Cameron McCord}\}\ \&\ \text{Group}\ \textit{IN}\ \{\text{M10, M11}\}\ \&\
\text{Room\_ID}\ \textit{IN} \{100, 101, 102,\\
103\}\ \&\ \text{Score}\ \textit{IN}\ \{70, 80, 90\})
\end{multline*}

@@

% Bibliography
\bibliographystyle{ACM-Reference-Format-Journals}
\bibliography{references}
                             % Sample .bib file with references that match those in
                             % the 'Specifications Document (V1.5)' as well containing
                             % 'legacy' bibs and bibs with 'alternate codings'.
                             % Gerry Murray - March 2012

% History dates
\received{February 2007}{March 2009}{June 2009}

\end{document}

>>>>

%% 
%% Copyright 2007, 2008, 2009 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%

%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%% SP 2008/03/01

\documentclass[preprint,12pt]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\author{Mosin Sergey, Zykin Sergey}
\usepackage{amssymb,amsmath}
\usepackage{amsthm}
%\usepackage{amsfonts}
%\usepackage{algorithm}
%\usepackage{xcolor}
%\usepackage{textcomp}
\newtheorem{note}{Note}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{statement}{Statement}
\def \eval #1#2{\left.#1\right\vert_{#2}}
\def \<#1> {\langle #1 \rangle}
\def \n #1{\mathit{#1}}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}

\journal{Theoretical Computer Science}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{Truth space method for caching database queries}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \address[label1]{}
%% \address[label2]{}

\author{S.~V. Mosin, S.~V. Zykin}

\address{Sobolev Institute of Mathematics of the Siberian Branch
of the Russian Academy of Sciences}

@@

\begin{keyword}
%% keywords here, in the form: keyword  keyword

%% PACS codes here, in the form: \PACS code \sep code

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
Relational databases \sep Caching \sep Truth space
\end{keyword}

\end{frontmatter}

%% \linenumbers

%% main text
\section{Introduction}
In this paper we discuss the use of data views that are
cached on the client's computer. We assume client-server environment with
server based Relational Database (RDB). The cache stores query results in order
to provide maximum usage of saved data in subsequent queries.

@@

Query 1: List of students studying physics, whose ID is bigger than 210:
$$P_1 = \pi_{X_1}(\sigma_{F_1} (R_1 \Join R_2)),$$
where $\pi_{X_1}$ -- projection operation over the set of attributes
$X_1 = \{\text{Stud\_ID},\\
\text{Stud\_Name}, \text{Group}, \text{Course}\}$,
$\sigma$ -- selecting operation,
$F_1$ -- logical formula: $(\text{Stud\_ID} > 210\ \&\ \text{Course} =
\text{Physics})$, $\Join$ --natural join.

Query 2: Examination sheets of the group M10:
$$P_2 = \pi_{X_2}(\sigma_{F_2} (R_1 \Join R_3)),$$
where
$X_2 = \{\text{Stud\_ID}, \text{Group}, \text{Course}, \text{Score}\}$, $F_2$
-- logical condition:\\
$(\text{Group}=\text{M10})$.

@@

\begin{multline*}
\mathcal{A} = Dom(\text{Stud\_ID})\times Dom(\text{Stud\_Name}) \times
Dom(\text{Group}) \times\\
Dom(\text{Room\_ID}) \times Dom(\text{Course}) \times Dom(\text{Score}) =
\{205, 315, 461\} \times \{\text{Rachel}\\
\text{Davis, Noam Angrist}, \text{Cameron McCord}\} \times\{\text{M10, M11}\}
\times \{100, 101, 102,\\
103\} \times \{\text{Physics, Chemistry}\} \times \{70, 80, 90\}
\end{multline*}

Obviously, without constraints this set represents more states than DB can have.
For example, each student has his/her own ID, whereas there are 3 corresponding
IDs for each student in $\mathcal{A}$: $\{205, 315, 461\}\times \{\text{Rachel
Davis},\\
\text{Noam Angrist, Cameron McCord}\}$.

@@

\begin{multline*}
F_1 = (\text{Stud\_ID} > 210\ \&\ \text{Course} = \text{Physics}\ \&\
\text{Stud\_Name}\ \textit{IN}\ \{\text{Rachel Davis},\\
\text{Noam Angrist, Cameron McCord}\}\ \&\ \text{Group}\ \textit{IN}\ \{\text{M10, M11}\}\ \&\
\text{Room\_ID}\ \textit{IN}\\ \{100, 101, 102, 103\}\ \&\ \text{Score}\ \textit{IN}\ \{70, 80, 90\})
\end{multline*}

@@

\bibliographystyle{elsarticle-num}
\bibliography{references}

\end{document}
\endinput
